Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-11-15 manuscript/manuscript.Rmd
Additional edits and tidying from Benedetto

A shift from targeted to untargeted metabolites may also in part explain why the increased biomass in the cyclone did not result in large increases in export [@Barone2022; @Bent2024]. Our list of known compounds covers a large fraction of the small molecules common to most organisms, indicating that unknown molecules are more likely to be rare and therefore more difficult to degrade. If the increased biomass in the cyclone is dominantly in the form of highly bioavailable compounds, it is not surprising that much of it can be easily degraded. This hypothesis is supported by @Gleich2024, who found that heterotrophy-associated transcripts were more abundant in the 2018 cruise cyclone than the anticyclone.

@@

The authors would like to thank the other members of the Ingalls Lab who provided assistance in sample processing, integration, and analysis. We are also grateful to the SCOPE science team (Tara Clemente and Tim Burrell) for sample collection during the Hawaiian Eddy Experiment. We would like to acknowledge the captain and crew of the R/V *Kilo Moana* and R/V *Falkor* during the KM1709 and FK180310 cruises for making this science possible. We would also like to acknowledge the analysts involved in the biogeochemical measurements for their willingness to provide data and answer questions (Eric Grabowski, Karin Bjorkman, and Rhea Foreman). This work was supported by grants from the Simons Foundation (SCOPE Award ID 329108 to AI, SF Award ID 385428 to AI, Postdoctoral Fellowship in Marine Microbial Ecology ID 548565 to WQ)

>>>>

A shift from targeted to untargeted metabolites may also in part explain why the increased biomass in the cyclone did not result in large increases in export [@Barone2022; @Bent2024]. Our list of known compounds covers a large fraction of the small molecules common to most organisms, indicating that unknown molecules are more likely to be rare and therefore more difficult to degrade or a result of prokaryote dominance. If the increased biomass in the cyclone is dominantly in the form of highly bioavailable compounds, it is not surprising that much of it can be easily degraded. This hypothesis is supported by @Gleich2024, who found that heterotrophy-associated transcripts were more abundant in the 2018 cruise cyclone than the anticyclone.

@@

The authors would like to thank the other members of the Ingalls Lab who provided assistance in sample processing, integration, and analysis. We are also grateful to the SCOPE science team (Tara Clemente and Tim Burrell) for sample collection during the Hawaiian Eddy Experiment. We would like to acknowledge the captain and crew of the R/V *Kilo Moana* and R/V *Falkor* during the KM1709 and FK180310 cruises for making this science possible. We would also like to acknowledge the analysts involved in the biogeochemical measurements for their willingness to provide data and answer questions (Eric Grabowski, Karin Bjorkman, and Rhea Foreman). This work was supported by grants from the Simons Foundation (SCOPE Award ID 329108 to AI, SF Award ID 385428 to AI, Postdoctoral Fellowship in Marine Microbial Ecology ID 548565 to WQ, and SCOPE Award ID 721264 to David Karl which supported BB).
